% !TEX TS-program = xelatex
% !TEX encoding = UTF-8
% !TeX spellcheck = en_GB

% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%

\input{conf/conf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Tommaso}{Papini}
\address{Via Poggio alla Croce 33, Figline e Incisa Valdarno, 50063, Florence, Italy}
\mobile{+39 3343621205} 
%%% Social
\email{tommy39@gmail.com}
% \homepage{www.homepage.com}
\github{oddlord}
\linkedin{tommaso-papini}
\skype{tommy39ita}
%%% Optionals
\position{Computer Engineer{\enskip\cdotp\enskip}Software Developer}
\quote{``Pursuing my biggest dream ever... Game Development!''}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Company Recruitment Team}
  {Company Name\\123 Fake Street\\Fake City, FK 12345}
\letterdate{\today}
\lettertitle{Job Application for Game Development}
% or Dear Mr./Ms./Dr. LastName,
\letteropening{Dear Sir or Madam,}
\letterclosing{Sincerely,}
% \letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Tommaso Papini~~~·~~~Cover Letter}
  {}

\begin{document}
  %%% Make a header for CV using personal data
  \makecvheader
  
  %%% Make a title for Cover Letter using letter data
  \makelettertitle
  
  %%% Write content for your cover letter
  \begin{cvletter}
    \cvparagraph{About Me}
      % Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.
    
      I'm a Software Developer, graduated in MS Computer Science with maximum score in Florence, Italy. After my graduation I started a period of academic research, during which I also started a PhD in quantitative analysis, but eventually I realised that research is not my path and decided to leave. I'm now actively pursuing my biggest passion of all time, Game Development. I've always been since young age a big videogames fan and I also love to code and develop all kinds of scripts and applications, which is why a career in the Game Development industry fills me with motivation and excitement. I also enjoy the idea of moving to a different place, learning new cultures and meeting new people (in the past, I have spent one year in Madrid, Spain, and another in Geneva, Switzerland, both times for training and working purposes).
    
    \cvparagraph{Why Company?}
      Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris a accumsan ligula. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Suspendisse vulputate sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis. Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus varius blandit.
    
    \cvparagraph{Why Me?}
      % Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. Ut interdum, enim varius pellentesque tincidunt, magna libero sodales tortor, ut fermentum nunc metus a ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat sit amet pulvinar diam venenatis.
      
      Although I have no past professional experience in the field of Game Development, I am very motivated and passionate about mastering the necessary skills. I've always demonstrated, both during my University career and my internship experiences, that I'm a hard worker and if I set a goal for myself, I always manage to find a solution and overcome any obstacle. I also consider myself a very adaptable person and in many occasions I have proved to be a very fast learner, even in contexts where I had no prior knowledge of the skills needed. Last but not least, I enjoy working in teams, collaborating with many people and giving my personal contribute in the development of a project.
  \end{cvletter}
  
  %%% Make a closing for Cover Letter using letter data
  \makeletterclosing
\end{document}
